### 2023-06-29 proofs/main.tex
Add soundness and completeness of unification Unification solution merge needs to be updated
WIP: finish merge lemmas
Restructure
Add term grammar
Add declarative typing
Add algorithmic typing
WIP: misc subtyping lemmas
wip

@@

@@

\subsection{Grammar}
\ottgrammartabular{
  \ottP\ottinterrule
  \ottN\ottinterrule
}

@@

\section{Multi-Quantified System}
\subsection{Grammar}
\ottgrammartabular{
  \ottiP\ottinterrule
  \ottiN\ottinterrule
}
\subsection{Declarative Subtyping}
\ottdefnsDOne

@@

\subsection{Normalization}
\subsubsection{Ordering}
\ottdefnsOrder

@@

@@

\subsection{Unification Solution Merge}

Unification solution is represented by a list of unification solution entries.
Each entry restricts an unification variable in two possible ways: either stating
that it must be equivalent to a certain type ($[[pua :≈ iP]]$ or $[[nua :≈
iN]]$) or that it must be a (positive) supertype of a certain type ($[[pua :≥
iP]]$).

@@

Two matching entries can be merged in the following way:
\begin{definition} \hfill \\
\ottdefnSME\\
\end{definition}
Notice that in case of equivalence, the assigned types
must be equal (i.e. alpha-equivalent) to be merged. This is because
the unification algorithm assumes that every type is normalized,
and hence, equivalence is alpha-equivalence 
(\cref{corollary:nf-complete-wrt-subt-equiv,corollary:nf-sound-wrt-subt-equiv}).

To merge two unification solution, we merge each pair of
matching entries, and unite the results.

\begin{definition}
  $\begin{aligned}[t]
  [[us1 & us2]] &= \{ [[usEntry1 & usEntry2]] \mid [[usEntry1]] \in [[us1]],
  [[usEntry2]]  \in [[us2]], \text{s.t. } [[usEntry1]] \text{ matches with }
                                   [[usEntry2]] \}\\
                &\cup
                                     \{ [[usEntry1]] \mid [[usEntry1]] \in
                                     [[us1]], \text{ s.t. }
                                     \forall [[usEntry2]]  \in [[us2]],
                                     [[usEntry1]] \text{ does not match with }
                                                     [[usEntry2]] \}\\
        &\cup
          \{ [[usEntry2]] \mid [[usEntry2]] \in
          [[us2]], \text{ s.t. }
          \forall [[usEntry1]]  \in [[us1]],
          [[usEntry1]] \text{ does not match with }
          [[usEntry2]] \}\\
   \end{aligned}$
\end{definition}

@@

@@

\subsection{Upper Bounds}

\input{../_build/_gen/tex/lub-lemmas.tex}

@@

\subsection{Solution Merge}
\input{../_build/_gen/tex/solution-merge-lemmas.tex}

\subsection{Subtyping Algorithm}
\input{../_build/_gen/tex/alg-subtyping-lemmas.tex}

>>>>

\newcommand{\depth}[1]{\mathsf{depth}(#1)}

@@

% Γ ⊢ scE1 & scE2 = scE3 :: :: E :: 'E'
\renewcommand{\ottdruleSCMESupSupName}[0]{$([[≥]]\&^{+}[[≥]])$}
\renewcommand{\ottdruleSCMEEqSupName}[0]{$([[≈]]\&^{+}[[≥]])$}
\renewcommand{\ottdruleSCMESupEqName}[0]{$([[≥]]\&^{+}[[≈]])$}
\renewcommand{\ottdruleSCMEPEqEqName}[0]{$([[≈]]\&^{+}[[≈]])$}
\renewcommand{\ottdruleSCMENEqEqName}[0]{$([[≈]]\&^{-}[[≈]])$}

% Γ ; Θ ⊨ uN ≈u iM ⫤ UC 
\renewcommand{\ottdruleUNVarName}[0]{(Var$^{-[[≈u]]}$)}
\renewcommand{\ottdruleUShiftUName}[0]{($\uparrow^{[[≈u]]}$)}
\renewcommand{\ottdruleUArrowName}[0]{($\rightarrow^{[[≈u]]}$)}
\renewcommand{\ottdruleUForallName}[0]{($\forall^{[[≈u]]}$)}
\renewcommand{\ottdruleUNUVarName}[0]{(UVar$^{-[[≈u]]}$)}

% Γ ; Θ ⊨ uP ≈u iQ ⫤ UC 
\renewcommand{\ottdruleUPVarName}[0]{(Var$^{+[[≈u]]}$)}
\renewcommand{\ottdruleUShiftDName}[0]{($\downarrow^{[[≈u]]}$)}
\renewcommand{\ottdruleUExistsName}[0]{($\exists^{[[≈u]]}$)}
\renewcommand{\ottdruleUPUVarName}[0]{(UVar$^{+[[≈u]]}$)}

% G ⊨ iP1 ≈au iP2 ⫤ ( Ξ , uQ , aus1 , aus2 )
\renewcommand{\ottdruleAUPVarName}[0]{(Var$^{+[[≈au]]}$)}
\renewcommand{\ottdruleAUShiftDName}[0]{($\downarrow^{[[≈au]]}$)}
\renewcommand{\ottdruleAUExistsName}[0]{($\exists^{[[≈au]]}$)}

% G ⊨ iN1 ≈au iN2 ⫤ ( Ξ , uM , aus1 , aus2 )
\renewcommand{\ottdruleAUNVarName}[0]{(Var$^{-[[≈au]]}$)}
\renewcommand{\ottdruleAUShiftUName}[0]{($\uparrow^{[[≈au]]}$)}
\renewcommand{\ottdruleAUForallName}[0]{($\forall^{[[≈au]]}$)}
\renewcommand{\ottdruleAUArrowName}[0]{($\rightarrow^{[[≈au]]}$)}
\renewcommand{\ottdruleAUAUName}[0]{(AU$^{-}$)}

@@

\subsection{Grammar}
\ottgrammartabular{
  \ottP\ottinterrule
  \ottN\ottinterrule
  \ottv\ottinterrule
  \ottc\ottinterrule
}

\subsection{Declarative Typing}
\ottdefnsDT

@@

\section{Multi-Quantified System}
\subsection{Grammar}
\ottgrammartabular{
  \ottiP\ottinterrule
  \ottiN\ottinterrule
}
\subsection{Declarative Multiquantified Subtyping}
\ottdefnsDOne

@@

\subsection{Normalization}

\subsubsection{Ordering}
\ottdefnsOrder

@@

\subsection{Singularity}
\ottdefnsSING

@@

\subsection{Constraint Merge}

Unification and subtyping constraints is are by a list of constraint entries.
Each entry restricts an unification variable in two possible ways: either
stating that it must be equivalent to a certain type ($[[pua :≈ iP]]$ or $[[nua
:≈ iN]]$) or that it must be a (positive) supertype of a certain type ($[[pua :≥ iP]]$).

@@

Two matching entries can be merged in the following way:
\begin{definition} \hfill \\
\ottdefnSCME\\
\end{definition}
% Notice that in case of equivalence, the assigned types
% must be equal (i.e. alpha-equivalent) to be merged. This is because
% the unification algorithm assumes that every type is normalized,
% and hence, equivalence is alpha-equivalence 
% (\cref{corollary:nf-complete-wrt-subt-equiv,corollary:nf-sound-wrt-subt-equiv}).

To merge two constraints, we merge each pair of
matching entries, and unite the results.
\ilyam{add contexts}
\begin{definition}
  $\begin{aligned}[t] [[SC1 & SC2]] &= 
    \{ [[scE1 & scE2]] \mid [[scE1]] \in [[SC1]], [[scE2]]  \in [[SC2]], \text{s.t. } [[scE1]] \text{ matches with } [[scE2]] \}\\
    &\cup 
    \{ [[scE1]] \mid [[scE1]] \in [[SC1]], \text{ s.t. } \forall [[scE2]]  \in [[SC2]], [[scE1]] \text{ does not match with } [[scE2]] \}\\
    &\cup 
    \{ [[scE2]] \mid [[scE2]] \in [[SC2]], \text{ s.t. } \forall [[scE1]]  \in [[SC1]], [[scE1]] \text{ does not match with } [[scE2]] \}\\
   \end{aligned}$
\end{definition}

\subsection{Constraint Satisfaction}
\ottdefnsSATSCE

@@

\subsection{Typing}
\ottdefnsAT

@@

\subsection{Unification Constraint Merge}
\input{../_build/_gen/tex/unif-constraint-merge-lemmas.tex}

@@

\subsection{Upper Bounds}
\input{../_build/_gen/tex/lub-lemmas.tex}

\subsection{Positive Subtyping}
\input{../_build/_gen/tex/alg-pos-subtyping-lemmas.tex}

\subsection{Subtyping Constraint Merge}
\input{../_build/_gen/tex/constraint-merge-lemmas.tex}

\subsection{Constraint Satisfaction}
\input{../_build/_gen/tex/constraint-sat-lemmas.tex}

\subsection{Negative Subtyping}
\input{../_build/_gen/tex/alg-neg-subtyping-lemmas.tex}

\subsection{Singularity}
\input{../_build/_gen/tex/singularity-lemmas.tex}

\subsection{Typing}
\input{../_build/_gen/tex/alg-typing-lemmas.tex}

### 2023-06-29 proofs/tex/alg-neg-subtyping-lemmas.tex
wip

\begin{lemma}[Soundness of Negative Subtyping] \label{lemma:neg-subt-soundness}
        If $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iM]]$, and $[[Γ ; Θ ⊢ uN]]$ then\\ 
        $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$
        implies $[[us : Θ|uv uN]]$ and 
        for any $[[us']]$ such that $[[Θ ⊢ us' ⇒ us]]$,
        $[[ Γ ⊢ [us']uN ≤ iM ]]$
\end{lemma}
\begin{proof}
    We prove it by induction on $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$.
    Let us consider the last rule to infer this judgment. 
    \begin{caseof}
        \item \ruleref{\ottdruleAArrowLabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$ has shape
        $[[G;Θ ⊨ uP → uN' ≤ iQ → iM' ⫤ us]]$\\
        On the next step, the the algorithm makes two recursive calls:
        $[[G;Θ ⊨ uP ≥ iQ ⫤ us1]]$ and $[[G;Θ ⊨ uN' ≤ iM' ⫤ us2]]$.
        By the soundness of positive subtyping (\cref{lemma:pos-subt-soundness}) and induction hypothesis, respectively 
        \begin{enumerate}
            \item $[[us1 : Θ | uv uP]]$ and $[[ Γ ⊢ [us1']uP ≥ iQ ]]$ for any $[[us1']]$ s.t. $[[Θ ⊢ us1' ⇒ us1]]$
            \item $[[us2 : Θ | uv uN']]$ and $[[ Γ ⊢ [us2']uN' ≤ iM' ]]$ for any $[[us2']]$ s.t. $[[Θ ⊢ us2' ⇒ us2]]$
        \end{enumerate}

        Then the algorithm merges two unification solutions $[[us1]]$ and $[[us2]]$.
        By \cref{lemma:merge-soundness}, since $[[uv uP ∪ uv uN' = uv (uP → uN')]]$, 
        we have $[[us1 & us2 : Θ | uv (uP → uN')]]$, and also
        $[[Θ ⊢ us1 & us2 ⇒ us1]]$ and $[[Θ ⊢ us1 & us2 ⇒ us2]]$.
        By the transitivity of solution weakening (\cref{lemma:weakening-transitivity}),
         $[[Θ ⊢ us' ⇒ us1 & us2]]$ implies $[[Θ ⊢ us' ⇒ us1]]$ and $[[Θ ⊢ us' ⇒ us2]]$.

% \[\begin{tikzcd}[arrows=Rightarrow]
% 	& {[[us']]} \\
% 	{[[us1]]} & {[[us1 & us2]]} & {[[us2]]}
% 	\arrow[from=2-2, to=2-3]
% 	\arrow[from=2-2, to=2-1]
% 	\arrow[from=1-2, to=2-2]
% \end{tikzcd}\]

        The application of the induction hypothesis gives us 
        $[[Γ ⊢ [us']uP ≥ iQ ]]$ and $[[ Γ ⊢ [us']uN' ≤ iM' ]]$.
        Finally, by \ruleref{\ottdruleDOneArrowLabel}, $[[Γ ⊢ [us'](uP → uN') ≤ iQ → iM']]$.

        \item \ruleref{\ottdruleANVarLabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$ has shape $[[G;Θ ⊨ a⁻ ≤ a⁻ ⫤ ·]]$\\
        This case is symmetric to \cref{case:pos-subt-soundness:var} of \cref{lemma:pos-subt-soundness}.

        \item \ruleref{\ottdruleAShiftULabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$ has shape $[[G;Θ ⊨ ↑uP ≤ ↑iQ ⫤ us]]$\\
        This case is symmetric to \cref{case:pos-subt-soundness:shift} of \cref{lemma:pos-subt-soundness}.

        \item \ruleref{\ottdruleAForallLabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us]]$ has shape $[[G;Θ ⊨ ∀pas.uN' ≤ ∀pbs.iM' ⫤ us]]$ s.t. either $[[pas]]$ or $[[pbs]]$ is not empty\\
        This case is symmetric to \cref{case:pos-subt-soundness:exists} of \cref{lemma:pos-subt-soundness}.

@@

\begin{lemma}[Completeness of the Negative Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iM]]$, $[[Γ ; Θ ⊢ uN]]$,
    $[[uN]]$ does not contain negative unification variables ($[[α̂⁻]] \notin [[uv uN]]$)
    and there exists $[[us : Θ | uv uN]]$ such that $[[ Γ ⊢ [us]uN ≤ iM ]]$.
    Then there exists $[[us']]$ such that $[[Γ ; Θ ⊨ uN ≤ iM ⫤ us']]$
    and $[[Θ ⊢ us ⇒ us']]$.
\end{lemma}
\begin{proof}
    We prove it by induction on $[[ Γ ⊢ [us]uN ≤ iM ]]$.
    Let us consider the last rule used in the derivation of $[[ Γ ⊢ [us]uN ≤ iM ]]$.
    \begin{caseof}
        \item $[[ Γ ⊢ [us]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneShiftULabel}\\
        Then $[[ uN ]] = [[ ↑uP ]]$, since
        the substitution $[[ [us]uN ]]$ must preserve the 
        top-level constructor of $[[uN]] \neq [[α̂⁻]]$ (since by assumption, $[[α̂⁻]] \notin [[uv uN]]$), 
        and $[[uQ]] = [[ ↓iM ]]$, and by inversion, $[[ Γ ⊢ [us]uN ≈ iM ]]$.
        The rest of the proof is symmetric to \cref{case:pos-subt-complete-upshift} of
         \cref{lemma:pos-subt-completeness}: notice that the algorithm does not make a recursive call, 
        and the difference in the induction statement for the positive and 
        the negative case here does not matter.

        \item $[[ Γ ⊢ [us]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneArrowLabel}, 
        i.e. $[[ [us]uN ]] = [[ [us]uP → [us]uN' ]]$ and $[[iM]] = [[iQ → iM']]$, 
        and by inversion, $[[ Γ ⊢ [us]uP ≥ iQ ]]$ and $[[ Γ ⊢ [us]uN' ≤ iM' ]]$.

        Let us consider restrictions of $[[us]]$ to 
        the set of unification variables in $[[uP]]$ and $[[uN']]$:
        $[[us | uv uP : Θ | uv uP]]$ and $[[us | uv uN' : Θ | uv uN']]$.
        Notice that 
        $[[ [us]uP = [us | uv uP]uP ]]$ and 
        $[[ [us]uN' = [us | uv uN']uN' ]]$.

       Let us apply the induction hypothesis to
       $[[ Γ ⊢ [us | uv uP]uP ≥ iQ ]]$ and
       $[[ Γ ⊢ [us | uv uN']uN' ≤ iM' ]]$ (notice that
       since $[[uv uN' ⊆ uv uN]]$, there are no negative unification variables in $[[uN']]$)
       to obtain $[[us'1]]$ and $[[us'2]]$ such that
       \begin{enumerate}
        \item $[[Γ; Θ ⊨ uP ≥ iQ ⫤ us'1]]$ and $[[Θ ⊢ us | uv uP ⇒ us'1]]$
        \item $[[Γ; Θ ⊨ uP ≥ iQ ⫤ us'2]]$ and $[[Θ ⊢ us | uv uN' ⇒ us'2]]$ 
       \end{enumerate}

       This way, the algorithm applies \ruleref{\ottdruleAArrowLabel}
       and terminates returning $[[us'1 & us'2]]$ as the result.

       It is left to show that $[[Θ ⊢ us ⇒ us'1 & us'2]]$.
       Since $[[us | uv uP ⊆ us]]$, 
       by \cref{lemma:weakening-monotonicity}, 
       $[[Θ ⊢ us ⇒ us | uv uP]]$,
       and then by transitivity (\cref{lemma:weakening-transitivity}), 
       $[[Θ ⊢ us ⇒ us'1]]$.
       Analogously, $[[Θ ⊢ us ⇒ us'2]]$.
       Then since by \cref{lemma:merge-completeness}, 
       $[[us'1 & us'2]]$ is the weakest restriction  
       implying both $[[us'1]]$ and $[[us'2]]$,
       we have $[[Θ ⊢ us ⇒ us'1 & us'2]]$, as required.

       \item \label{case:subt-complete-forall}
       $[[ Γ ⊢ [us]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneForallLabel}.
       Since $[[uN]]$ does not contain negative unification variables,
       $[[uN]]$ must be of the form $[[∀pas.uN']]$,
       such that $[[ [us]uN = ∀pas.[us]uN' ]]$ and $[[ [us]uN']] \neq [[∀]]\dots$
       (assuming $[[pas]]$ does not intersect with the range of $[[us]]$).
       Also, $[[iM]] = [[∀pbs.iM']]$ and either $[[pas]]$ or $[[pbs]]$ is non-empty.

@@

       \item $[[ Γ ⊢ [us]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneNVarLabel}.\\
       Then $[[iN]] = [[ [us]uN ]] = [[ α⁻ ]] = [[iM]]$. 
       Here the first equality holds because $[[uN]]$ is not a unification variable:
       by assumption, $[[uN]]$ is free of negative unification variables.
       The second and the third equations hold because \ruleref{\ottdruleDOneNVarLabel}
       was applied.

>>>>

\begin{lemma}[Soundness of Negative Subtyping] \label{lemma:neg-subt-soundness}
        If $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iM]]$, $[[Γ ; Θ ⊢ uN]]$ and 
        $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$, then 
        $[[Θ ⊢ SC]]$ and 
        for any normalized $[[uσ]]$ such that $[[Θ ⊢ uσ : SC]]$,
        $[[ Γ ⊢ [uσ]uN ≤ iM ]]$.
\end{lemma}
\begin{proof}
    We prove it by induction on $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$.

    Suppose that $[[uσ]]$ is normalized and $[[Θ ⊢ uσ : SC]]$,
    Let us consider the last rule to infer this judgment. 
    \begin{caseof}
        \item \ruleref{\ottdruleAArrowLabel}. Then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$ has shape
        $[[G;Θ ⊨ uP → uN' ≤ iQ → iM' ⫤ SC]]$\\
        On the next step, the the algorithm makes two recursive calls:
        $[[G;Θ ⊨ uP ≥ iQ ⫤ SC1]]$ and $[[G;Θ ⊨ uN' ≤ iM' ⫤ SC2]]$
        and returns $[[Θ ⊢ SC1 & SC2 = SC]]$ as the result.

        By the soundness of constraint merge (\cref{lemma:merge-soundness}),
        $[[Θ ⊢ uσ : SC1]]$ and $[[Θ ⊢ uσ : SC2]]$.
        Then by the soundness of positive subtyping (\cref{lemma:pos-subt-soundness}), $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$; 
        and by the induction hypothesis, $[[ Γ ⊢ [uσ]uN' ≤ iM' ]]$.
        This way, by \ruleref{\ottdruleDOneArrowLabel}, $[[Γ ⊢ [uσ](uP → uN') ≤ iQ → iM']]$.

        \item \ruleref{\ottdruleANVarLabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$ has shape $[[G;Θ ⊨ a⁻ ≤ a⁻ ⫤ ·]]$\\
        This case is symmetric to \cref{case:pos-subt-soundness:var} of \cref{lemma:pos-subt-soundness}.

        \item \ruleref{\ottdruleAShiftULabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$ has shape $[[G;Θ ⊨ ↑uP ≤ ↑iQ ⫤ SC]]$\\
        This case is symmetric to \cref{case:pos-subt-soundness:shift} of \cref{lemma:pos-subt-soundness}.

        \item \ruleref{\ottdruleAForallLabel}, and then $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$ has shape
         $[[G;Θ ⊨ ∀pas.uN' ≤ ∀pbs.iM' ⫤ SC]]$ s.t. either $[[pas]]$ or $[[pbs]]$ is not empty\\
        This case is symmetric to \cref{case:pos-subt-soundness:exists} of \cref{lemma:pos-subt-soundness}.

@@

\begin{lemma}[Completeness of the Negative Subtyping]
    Suppose that $[[Γ ⊢ Θ]]$, $[[Γ ⊢ iM]]$, $[[Γ ; Θ ⊢ uN]]$,
    and $[[uN]]$ does not contain negative unification variables ($[[α̂⁻]] \notin [[uv uN]]$).
    Then for any $[[Θ ⊢ uσ]]$ such that $[[Γ ⊢ [uσ]uN ≤ iM]]$,
    there exists $[[Γ ; Θ ⊨ uN ≤ iM ⫤ SC]]$, such that $[[Θ ⊢ SC]]$ and moreover, $[[Θ ⊢ uσ : SC]]$.
\end{lemma}
\begin{proof}
    We prove it by induction on $[[ Γ ⊢ [uσ]uN ≤ iM ]]$.
    Let us consider the last rule used in the derivation of $[[ Γ ⊢ [uσ]uN ≤ iM ]]$.
    \begin{caseof}
        \item $[[ Γ ⊢ [uσ]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneShiftULabel}\\
        Then $[[ uN ]] = [[ ↑uP ]]$, since
        the substitution $[[ [uσ]uN ]]$ must preserve the 
        top-level constructor of $[[uN]] \neq [[α̂⁻]]$ (since by assumption, $[[α̂⁻]] \notin [[uv uN]]$), 
        and $[[uQ]] = [[ ↓iM ]]$, and by inversion, $[[ Γ ⊢ [uσ]uN ≈ iM ]]$.
        The rest of the proof is symmetric to \cref{case:pos-subt-complete-upshift} of
         \cref{lemma:pos-subt-completeness}: notice that the algorithm does not make a recursive call, 
        and the difference in the induction statement for the positive and 
        the negative case here does not matter.

        \item $[[ Γ ⊢ [uσ]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneArrowLabel}, 
        i.e. $[[ [uσ]uN ]] = [[ [uσ]uP → [uσ]uN' ]]$ and $[[iM]] = [[iQ → iM']]$, 
        and by inversion, $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$ and $[[ Γ ⊢ [uσ]uN' ≤ iM' ]]$.

        The algorithm makes two recursive calls: $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC1]]$ and $[[Γ ; Θ ⊨ uN' ≤ iM' ⫤ SC2]]$,
        and then returns $[[Θ ⊢ SC1 & SC2 = SC]]$ as the result.
        Let us show that these recursive calls are successful and the returning constraints 
        are fulfilled by $[[uσ]]$.

        Notice that from the inversion of $[[Γ ⊢ iM]]$, we have: $[[Γ ⊢ iQ]]$ and $[[Γ ⊢ iM']]$;
        from the inversion of $[[Γ ; Θ ⊢ uN]]$, we have: $[[Γ ; Θ ⊢ uP]]$ and $[[Γ ; Θ ⊢ uN']]$;
        and since $[[uN]]$ does not contain negative unification variables,
        $[[uN']]$ does not contain negative unification variables either.

        This way, we can apply the induction hypothesis to $[[Γ ⊢ [uσ]uN' ≤ iM']]$ to 
        obtain $[[Γ ; Θ ⊨ uN' ≤ iM' ⫤ SC2]]$ such that $[[Θ ⊢ SC2]]$ and $[[Θ ⊢ uσ : SC2]]$.
        Also, we can apply the completeness of the positive subtyping (\cref{lemma:pos-subt-completeness}) to 
        $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$ to obtain $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC1]]$ such that $[[Θ ⊢ SC1]]$ and $[[Θ ⊢ uσ : SC1]]$.

        Finally, we need to show that the merge of $[[SC1]]$ and $[[SC2]]$ is successful and
        satisfies the required properties.
        To do so, we apply the completeness of subtyping constraint merge (\cref{lemma:merge-completeness}).
        This way, $[[Θ ⊢ SC1 & SC2 = SC]]$ is defined, $[[Θ ⊢ SC]]$, and $[[Θ ⊢ uσ : SC]]$, as required.

       \item \label{case:subt-complete-forall}
       $[[ Γ ⊢ [uσ]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneForallLabel}.
       Since $[[uN]]$ does not contain negative unification variables,
       $[[uN]]$ must be of the form $[[∀pas.uN']]$,
       such that $[[ [uσ]uN = ∀pas.[uσ]uN' ]]$ and $[[ [uσ]uN']] \neq [[∀]]\dots$
       (assuming $[[pas]]$ does not intersect with the range of $[[uσ]]$).
       Also, $[[iM]] = [[∀pbs.iM']]$ and either $[[pas]]$ or $[[pbs]]$ is non-empty.

@@

       \item $[[ Γ ⊢ [uσ]uN ≤ iM ]]$ is derived by \ruleref{\ottdruleDOneNVarLabel}.\\
       Then $[[iN]] = [[ [uσ]uN ]] = [[ α⁻ ]] = [[iM]]$. 
       Here the first equality holds because $[[uN]]$ is not a unification variable:
       by assumption, $[[uN]]$ is free of negative unification variables.
       The second and the third equations hold because \ruleref{\ottdruleDOneNVarLabel}
       was applied.
